---
title: "ecommerce script"
author: "Eleanor Pulsipher, Sarah Hellmann, Isabel de Obaldia, Ryan Boden"
date: "11/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages Used:
```{r message=FALSE}
library(haven)
library(tidyr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(janitor)
library(ggpubr)
```

To Make a trimmed dataframe:
```{r, message=FALSE}
ecommerce <- read_csv("Ecommerce_dataset.csv")

ecommerce_trimmed <- ecommerce %>% select(order_total_items, order_id, product_id, seller_id, order_price, order_freight_value, order_value, payment_type, payment_installments, main_payment_method, avg_review_score, order_est_delivery_date, order_delivered_time, order_delivered_date, customer_id, customer_zip_code_prefix, customer_city, customer_state, product_description_lenght, product_photos_qty, distance, category_D1, category_D2, category_D3, category_D4, category_D5, category_D6, product_height_cm, product_weight_g, product_length_cm, product_width_cm)
```
**Interesting Findings and Recommendations 1 and 2**

By product id (which are the most ordered products)
```{r, message=FALSE}
by_product_id <- ecommerce %>%
  group_by(product_id)%>%
  summarise(count =n())%>%
  arrange(desc(count))
```
By seller id (which sellers are the most active)
```{r, message=FALSE}
by_seller_id <- ecommerce%>%
  group_by(seller_id)%>%
  summarise(count = n())%>%
  arrange(desc(count))
```
Average review score in products (average review score across all products)
```{r}
overall_avg_review_score <- mean(ecommerce$avg_review_score, na.rm= T)
```
By customer location (from which cities do most customers order from)
```{r, message=FALSE}
by_location <- ecommerce%>%
  group_by(customer_city)%>%
  summarise(count=n())%>%
  arrange(desc(count))
```
Approximation of number of products ordered per city
```{r, message=FALSE}
products_locations <- ecommerce%>%
  group_by(customer_city, single_product)%>%
  summarize(product_sum= sum(single_product))
```
By customer state (from which states do most customers order from)
```{r, message=FALSE}
by_state <- ecommerce%>%
  group_by(customer_state)%>%
  summarise(count=n())%>%
  arrange(desc(count))
```
Customer Unique ID
```{r, message=FALSE}
by_unique_id <- ecommerce%>%
  group_by(customer_unique_id, avg_review_score)%>%
  summarise(count=n())
```
Average review scores
```{r}
avg_review_score_5<-filter(by_unique_id, avg_review_score == 5)
avg_review_score_4<-filter(by_unique_id, avg_review_score == 4)
avg_review_score_3<-filter(by_unique_id, avg_review_score == 3)
avg_review_score_2<-filter(by_unique_id, avg_review_score == 2)
avg_review_score_1<-filter(by_unique_id, avg_review_score == 1)
```
By Product Category
```{r, message=FALSE}

product_category <- ecommerce%>%
                  group_by(product_category_name)%>%
                  summarise(count=n())%>%
                  arrange(desc(count))
```
By seller city and state

```{r, message=FALSE}
by_seller_city <- ecommerce%>%
                group_by(seller_city)%>%
                summarize(count=n())%>%
                arrange(desc(count))

by_seller_state <- ecommerce%>%
  group_by(seller_state)%>%
  summarize(count=n())%>%
  arrange(desc(count))
```


Satisfaction scores of top products 
``` {r}
ecommerce%>% 
  filter(product_category_name == 'cama_mesa_banho')%>%
  summarize(avg_satisfaction = mean(avg_review_score))

ecommerce%>% 
  filter(product_category_name == 'beleza_saude')%>%
  summarize(avg_satisfaction = mean(avg_review_score))

ecommerce%>% 
  filter(product_category_name == 'esporte_lazer')%>%
  summarize(avg_satisfaction = mean(avg_review_score))


ecommerce%>% 
  filter(product_category_name == 'informatica_acessorios')%>%
  summarize(avg_satisfaction = mean(avg_review_score))


ecommerce%>% 
  filter(product_category_name == 'moveis_decoracao')%>%
  summarize(avg_satisfaction = mean(avg_review_score))


ecommerce%>% 
  filter(product_category_name == 'utilidades_domesticas')%>%
  summarize(avg_satisfaction = mean(avg_review_score))


ecommerce%>% 
  filter(product_category_name == 'relogios_presentes')%>%
  summarize(avg_satisfaction = mean(avg_review_score))

ecommerce%>% 
  filter(product_category_name == 'telefonia')%>%
  summarize(avg_satisfaction = mean(avg_review_score))


ecommerce%>% 
  filter(product_category_name == 'automotivo')%>%
  summarize(avg_satisfaction = mean(avg_review_score))

ecommerce%>% 
  filter(product_category_name == 'brinquedos')%>%
  summarize(avg_satisfaction = mean(avg_review_score))
```


**Recommendation 3 -**
To add shipping disparity variable:
```{r}
ecommerce_trimmed <- ecommerce_trimmed %>% mutate(shipping_disparity = order_est_delivery_date-order_delivered_date)

ecommerce_trimmed$shipping_disparity <- as.numeric(ecommerce_trimmed$shipping_disparity, units="days")
```
To find summary statistics for disparity:
```{r}
disparity_summary <- ecommerce_trimmed %>% filter(!is.na(shipping_disparity)) %>% summarise(avg_shipping_disparity = mean(shipping_disparity), median_shipping_disparity = median(shipping_disparity), max_shipping_disparity = max(shipping_disparity), min_shipping_disparity = min(shipping_disparity), sd_time_disparity = sd(shipping_disparity), IQR_disparity = IQR(shipping_disparity))

print(disparity_summary)
```
Linear regression for disparity: 
```{r fig.width = 7, fig.height = 2.69, dpi = 96}
library(regress)
library(sandwich)
library(survival)
shipping_result <- regress(
  ecommerce_trimmed, 
  rvar = "shipping_disparity", 
  evar = c(
    "order_price", "order_freight_value", "customer_state", 
    "distance", "product_height_cm", "product_weight_g", "product_length_cm", 
    "product_width_cm"
  )
)

```
To create "northeast" factor variable:
```{r}
ecommerce_trimmed <-  mutate(ecommerce_trimmed, Northeast = ifelse(customer_state %in% 'AL'|customer_state %in% 'BA'|customer_state %in% 'CE'| customer_state %in% 'MA'| customer_state %in% 'PA'|customer_state %in% 'PB'|customer_state %in% 'PE'|customer_state %in% 'PI'|customer_state %in% 'RN'|customer_state %in% 'RR'|customer_state %in% 'SE'|customer_state %in% 'TO', "1", "0"))

ecommerce_trimmed$Northeast <- factor(ecommerce_trimmed$Northeast)
```
T-test 1: northeast and review scores:
```{r fig.width = 7, fig.height = 4.31, dpi = 96}
library(ggpubr)
result <- compare_means(
  data=ecommerce_trimmed, 
  var1 = "Northeast", 
  var2 = "avg_review_score", 
  alternative = "greater"
)
summary(result, show = FALSE)
```
T-test 2: northeast and shipping disparity
```{r fig.width = 7, fig.height = 4.31, dpi = 96}
result <- compare_means(
  data = ecommerce_trimmed, 
  var1 = "Northeast", 
  var2 = "shipping_disparity", 
  alternative = "greater"
)
summary(result, show = FALSE)
```

**Recommendation 4 - **
Summary stats for Payment types:
```{r, message=FALSE}
payment_summary <- ecommerce_trimmed %>% group_by(main_payment_method) %>% summarise(mean_order_revenue = mean(order_price), mean_items_ordered = mean(order_total_items), mean_satisfaction_score = mean(avg_review_score))
```

voucher t test for order value:
```{r fig.width = 7, fig.height = 4.31, dpi = 96}
result <- compare_means(
  data = ecommerce_trimmed, 
  var1 = "main_payment_method", 
  var2 = "order_value", 
  alternative = "greater", 
  conf_lev = 0.97
)
summary(result, show = FALSE)
plot(result, plots = "scatter", custom = FALSE)
```

voucher t test for items ordered
```{r fig.width = 7, fig.height = 4.31, dpi = 96}
result <- compare_means(
  data=ecommerce_trimmed, 
  var1 = "main_payment_method", 
  var2 = "order_total_items", 
  alternative = "greater", 
  conf_lev = 0.97
)
summary(result, show = FALSE)
plot(result, plots = "scatter", custom = FALSE)
```

voucher t test for review scores
```{r fig.width = 7, fig.height = 4.31, dpi = 96}
result <- compare_means(
  data=ecommerce_trimmed, 
  var1 = "main_payment_method", 
  var2 = "avg_review_score", 
  alternative = "greater", 
  conf_lev = 0.97
)
summary(result, show = FALSE)
```

**Recommendation 5**

```{r}
library(haven)
#Data frame of count of category purchases by state:
#Category 1: Auto and Industrial
cat1 <- ecommerce %>% 
  select(customer_state, category_D1) %>%
  group_by(customer_state) %>%
  filter(category_D1 == 1) %>%
  count() %>%
  rename(Auto.Industrial = n)
cat1 <- as.data.frame(cat1)

#Category 2: books
cat2 <- ecommerce %>%
  select(customer_state, category_D2) %>%
  group_by(customer_state) %>%
  filter(category_D2 == 1) %>%
  count() %>%
  rename(Books = n) 
cat2 <- as.data.frame(cat2)
#missing in cat2(books): AP (row 4), RR (row 22)
cat2addrow4 <- cat2 %>%
  add_row(customer_state = 'AP', Books = 0, .before = 4)
cat2complete <- cat2addrow4 %>%
  add_row(customer_state = 'RR', Books = 0, .before = 22)

#Category 3: Electronics
cat3 <- ecommerce %>%
  select(customer_state, category_D3) %>%
  group_by(customer_state) %>%
  filter(category_D3 == 1) %>%
  count()  %>%
  rename(Electronics = n)
cat3 <- as.data.frame(cat3)

#Category 4: Fashion
cat4 <- ecommerce %>%
  select(customer_state, category_D4) %>%
  group_by(customer_state) %>%
  filter(category_D4 == 1) %>%
  count()  %>%
  rename(Fashion = n)
cat4 <- as.data.frame(cat4)

#Category 5: Home Goods
cat5 <- ecommerce %>%
  select(customer_state, category_D5) %>%
  group_by(customer_state) %>%
  filter(category_D5 == 1) %>%
  count()  %>%
  rename(HomeGoods = n)
cat5 <- as.data.frame(cat5)

#Category 6: Office
cat6 <- ecommerce %>%
  select(customer_state, category_D6) %>%
  group_by(customer_state) %>%
  filter(category_D6 == 1) %>%
  count()  %>%
  rename(Office = n)
cat6 <- as.data.frame(cat6)

#Combine categories:
categoriesCombined <- cbind(cat1, cat2complete, cat3, cat4, cat5, cat6)

#Change row names and drop state columns:
row.names(categoriesCombined) <- categoriesCombined[ ,1]
categoriesByState <- categoriesCombined[,-c(1,3,5,7,9,11)]

#Data as a matrix:
categoriesByState.mat <- as.matrix(categoriesByState)

#CLUSTERING:
#dist matrix:
d <- dist(categoriesByState.mat)
#Clustering Algorithm:
c <- hclust(d)
#Plot the Dendrogram:
plot(c)
#Cut into K:
cut <-  cutree(c, k = 5)
dfCut <- as.data.frame(cut)
```

**Recommendation 6**

installments summary statistics:
```{r}
installments_summary <- ecommerce_trimmed %>% summarise(avg_installments = mean(payment_installments), median_installments = median(payment_installments), max_installments = max(payment_installments), IQR_installments = IQR(payment_installments), sd_installments = sd(payment_installments))
print(installments_summary)
```

Regression between installments and satisfaction scores:
```{r fig.width = 7, fig.height = 2.69, dpi = 96}
installments_effect <- regress(
  ecommerce_trimmed, 
  rvar = "avg_review_score", 
  evar = "payment_installments"
)
summary(result, conf_lev = 0.96)
```

To create long_payment variable:
```{r}
ecommerce_trimmed <- mutate(ecommerce_trimmed, Long_Payment = ifelse(payment_installments > 11, "1", "0"))
```

To compare long payment satisfaction mean:
```{r}
long_mean <- ecommerce_trimmed %>% filter(Long_Payment == 1) %>% summarise(mean_satisfaction = mean(avg_review_score))

short_mean <- ecommerce_trimmed %>% filter(Long_Payment == 0) %>% summarise(mean_satisfaction = mean(avg_review_score))

short_mean > long_mean
```

**Recommendation 7**
```{r}
str(ecommerce)

options(scipen = 999, digits=3)


ecommerce$review_score <- as.integer(ecommerce$review_score)
ecommerce$product_photos_qty <- as.integer(ecommerce$product_photos_qty)


test <- glm(formula= review_score ~ product_photos_qty, data=ecommerce, na.action = na.omit)

summary(test)
exp(0.01163)

#As Photo Quantity by 1, the odds of buying increase 1%.

ecommerce %>% 
  summarize(max_photos = max(product_photos_qty, na.rm=T), mean_photos = mean(product_photos_qty, na.rm = T), min_photos = min(product_photos_qty, na.rm = T))

ecom1 <- ecommerce %>% 
  transmute(product_photos_qty, review_score) %>% 
  group_by(product_photos_qty) %>% 
  transmute(product_photos_qty, review_score)

ecom2 <- na.omit(ecom1)

j <- table(ecom2$product_photos_qty)
j

48028 * .01

#NA data
(nrow(ecommerce) - sum(j)) / sum(j)

#Percentages
k <- j[1:6]/nrow(j)
sum(k) + (nrow(ecommerce) - sum(j)) / sum(j)

z <- j[7:19]/sum(j)
1-sum(z)
```


